Push-Pull Signal-Function Functional Reactive Programming

### 2012-08-29 Docs/IFL2012/presentation/presentation.tex
Presentation source update

\title{Push-Pull Signal-Function Functional Reactive Programming}
\author{Edward Amsden}
\institute{Rochester Institute of Technology}

@@

\AtBeginSection[]
{
\begin{frame}
\frametitle{\insertsection}
\end{frame}
}

@@

\begin{frame}
\frametitle{Functional Reactive Programming (FRP)}
    \begin{itemize}
        \item {\em Functional} First-class and higher-order functions.
        \item {\em Reactive} Behavior changes in response to temporal inputs.
        \item Basic abstractions
        \begin{itemize}
            \item Signals - Functions of time\footnote{Often also called behaviors.}.
            \item Events - Sequences of temporally ordered and labeled discrete values.
        \end{itemize}
    \end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Push vs. Pull Evaluation}
    \begin{itemize}
        \item When to evaluate what?
        \item Pull evaluation: (``demand-driven'') Evaluate when output is needed.
        \item Push evaluation: (``data-driven'') Evaluate when input is available.
        \item Ideally, FRP uses both: pull for signals and push for events.
    \end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Combinator Implementations: Serial Composition ({\tt >>>})}
    \begin{itemize}
        \item Initialization:
        \item Running:
    \end{itemize}
\end{frame}

\begin{frame}
\frametitle{Combinator Implementations: Parallel Composition ({\tt first})}
    \begin{itemize}
        \item Initialization:
        \item Running:
    \end{itemize}
\end{frame}

\begin{frame}
\frametitle{Combinator Implementations: Parallel Composition ({\tt second})}
    \begin{itemize}
        \item Initialization:
        \item Running:
    \end{itemize}
\end{frame}

\begin{frame}
\frametitle{Time-independence optimization}
\end{frame}

\begin{frame}
\frametitle{Event Merging}
\end{frame}

>>>>

\title{Push-Pull Signal-Function Functional Reactive Programming}
\author{Edward Amsden}
\institute{Rochester Institute of Technology}
\date{IFL 2012\\ \today}

@@

\AtBeginSection[]
{
\begin{frame}
\end{frame}
}

@@

\begin{frame}
\frametitle{Functional Reactive Programming (FRP)}
    \begin{itemize}
        \item {\em Functional} First-class and higher-order functions.
        \item {\em Reactive} Behavior changes in response to temporal inputs.
        \item Basic abstractions:
        \begin{itemize}
            \item Signals - Functions of time\footnote{Often also called behaviors.}.
            \item Events - Sequences of temporally ordered and labeled discrete values.
        \end{itemize}
    \end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Push vs. Pull Evaluation}
    \begin{itemize}
        \item When to evaluate what?
        \item Pull evaluation (``demand-driven''):\\ Evaluate when output is needed.
        \item Push evaluation (``data-driven''):\\ Evaluate when input is available.
        \item Ideally, an FRP system uses push for events and pull for signals\footcite{Elliott2009}.
    \end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Time-independence optimization}
    \begin{itemize}
        \item Inefficiency: running every time continuation every sample step.
        \item This happens even if the signal delta is empty (no change)
        \item Currently this is necessary because the {\em time} delta might
              cause some output.
        \item Optimization:
        \begin{itemize}
            \item Mark time-independent SFs using a separate constructor.
            \item "Smart" composition-routing to make a composite SF time-independent
                  if all of its components are.
            \item Time-independent time continuation has no time input, only delta.
            \item Only called if non-empty delta. 
        \end{itemize}
    \end{itemize}
\end{frame}

\begin{frame}
\frametitle{Event Merging (Semantics Idea)}
    \begin{itemize}
        \item Push-based events are not tied to samples.
        \item We thus know only what the last sample time was for an event,
              not the actual time.
        \item Can we hide event merging in this loss of precision?
    \end{itemize}
\end{frame}
